---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggplot2)
library(ggsignif)
library(ggbeeswarm)
library(grid)
library(gridExtra)
library(tidyverse)
library(broom)
```


```{r fig1, fig.height=7, fig.width=11}


data=read.csv('CD8-Tcells/boxplots/AB_FMBA_weighted_sum_top_5000AA.tsv', sep="\t", header=TRUE)
data$COHORT=factor(data$COHORT,  
                   levels=c("Adaptive", "HIP", "KECK", "fmba_covid", "fmba_healthy", "fmba_precovid"))

kruskal.res=data  %>% 
  group_by(dataset) %>% 
  summarise(fit = list(kruskal.test(WEIGHT_SUM ~ COHORT) %>% tidy)) %>% 
  unnest_wider(fit)
#kruskal.res.ab=round(log10(kruskal.res$p.value[1]))
#kruskal.res.fmba=round(log10(kruskal.res$p.value[2]))
data$dataset=factor(data$dataset, levels=c("Adaptive", "FMBA"))
medi=median(log10(data$WEIGHT_SUM))
#data %>% group_by(dataset) %>%
ggplot(data,aes(x=COHORT, y=log10(WEIGHT_SUM))) +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#  geom_quasirandom(method = 'pseudorandom', aes(colour=COHORT), size = 2) +
#  geom_hline(yintercept=medi, linetype = "dashed") +
  geom_boxplot(notch=FALSE, outlier.size = 0.7, lwd=0.7, alpha = 0) +
  geom_signif(
    comparisons = list(c("Adaptive", "HIP"), c("COVID", "HEALTHY"),
                       c("Adaptive", "KECK"), c("COVID","PRECOVID")),
    map_signif_level = TRUE, textsize = 3) +
  ylim(-5.5, 0) +
  scale_color_brewer(palette = "Set2") +
  theme_light() +              
  theme(legend.position = "none",text=element_text(size=10,  family="Comic Sans MS")) +
  labs(y= "log10(Fraction)", x = "samples") 

```
```


```{r fig1, fig.height=7, fig.width=11}


data=read.csv('../feature_search/wilcox_test/BOXPLOTS/FREQ/Adaptive_FMBA_top_5000AA/Adaptive_FMBA_associated_clones_thomas_clusters.tsv', sep="\t", header=TRUE)
data$COHORT=factor(data$COHORT,  
                   levels=c("Adaptive", "HIP", "KECK", "COVID", "HEALTHY", "PRECOVID"))

kruskal.res=data  %>% 
  group_by(dataset) %>% 
  summarise(fit = list(kruskal.test(WEIGHT_SUM ~ COHORT) %>% tidy)) %>% 
  unnest_wider(fit)
#kruskal.res.ab=round(log10(kruskal.res$p.value[1]))
#kruskal.res.fmba=round(log10(kruskal.res$p.value[2]))
data$dataset=factor(data$dataset, levels=c("Adaptive", "FMBA"))
data$tcrdist120_cluster_id=factor(data$tcrdist120_cluster_id, levels=c("13", "36", "29", "23", "2","4"))
#medi=median(log10(data$WEIGHT_SUM))
#data %>% group_by(dataset) %>%
ggplot(data,aes(x=COHORT, y=log10(WEIGHT_SUM))) +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#  geom_quasirandom(method = 'pseudorandom', aes(colour=COHORT), size = 2) +
#  geom_hline(yintercept=medi, linetype = "dashed") +
  geom_boxplot(notch=FALSE, outlier.size = 0.7, lwd=0.7, alpha = 0) +
  geom_signif(
    comparisons = list(c("Adaptive", "HIP"), c("COVID", "HEALTHY"),
                       c("Adaptive", "KECK"), c("COVID","PRECOVID")),
    map_signif_level = TRUE, textsize = 3) +
  facet_wrap(~tcrdist120_cluster_id) +
  ylim(-5.5, 0) +
  scale_color_brewer(palette = "Set2") +
  theme_light() +              
  theme(legend.position = "none",text=element_text(size=10,  family="Comic Sans MS")) +
  labs(y= "log10(Fraction)", x = "samples") 

```

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
